full title

### 2020-11-21 paper/pldi21/ds.tex
Till Sec. 3.6

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.15\textwidth}
    \includegraphics[height=3.2cm]{img/listing}
    \caption{Notations}
    \label{fig:ds-example1}
  \end{subfigure}
  \quad
  \begin{subfigure}[t]{0.23\textwidth}
    \includegraphics[height=3.2cm]{img/path-1}
    \caption{$\varx = 0$}
    \label{fig:ds-example2}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{img/path-2}
    \caption{$\varx > 0$}
    \label{fig:ds-example3}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{img/path-3}
    \caption{$\varx \in \mathbb{N}$}
    \label{fig:ds-example4}
  \end{subfigure}
  \caption{Three abstract interpretation using combined domain for the running
  example with different initial values for $\varx$.}
  \label{fig:ds-examples}
\end{figure*}

@@

\subsection{Examples}

For examples of the abstract interpretation with the combined domain,
Figure~\ref{fig:ds-examples} depicts the flow of analysis for the running
example in Figure~\ref{fig:running-example} with three different initial set of
values for the variable $\varx$.  In this example, we use the abstract domain
$\{ -, 0, + \}$ for integers stored in $\varx$ introduced in
Section~\ref{sec:ai}, and the \textit{flow sensitivity} which utilizes the
labels of states as their views introduced in Section~\ref{sec:sens}.  For
brevity, we use the concatenated form to represent the abstract values such as
$-0$ denotes the set $\{ -, 0 \}$.

Figure~\ref{fig:ds-examples}(a) explains notations used in each graph. A solid
box denotes an analysis element, which is a pair of label $\lab$ and abstract
state $\abselem$.  A pair wrapped with angle brackets denotes an analysis
element, which is a pair of abstract instantiation map $\absimap$ and sealed
symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
each pair in graphs contains only the value of the variable of $\varx$ without
the current label.  For brevity, we represents its label by locating them in the
next to the corresponding label.  A solid line is a view transition
$\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
line is a sealed symbolic transition $\symbtrans$.  Three solid lines with
circled labels denote two converters $\saconverter$, $\asconverter$ and the join
operator $\join$.

Figure~\ref{fig:ds-examples}(b) shows the analysis with the combined domain when
the initial value of $\varx$ is $0$.  First, in the \triagename step,
the converter $\asconverter$ converts the analysis element $(\lab_0, 0)$ to
another analysis element $\langle \varnothing, 0 \rangle$ with the label
$\lab_0$.  Moreover, it does not introduce any sealed symbolic values because
the value represents only a single value.  Until the end of the program, the
sealed symbolic execution from $\langle \varnothing, 0 \rangle$ is successfully
continues.  However, there is no more possible symbolic transition for the
symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$.  Thus,
it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.

Instead of a single value, assume that the initial value of $\varx$ is one of
any positive integers.  Figure~\ref{fig:ds-examples}(c) describes the analysis
flow for such case.  Then, the initial abstract value at the label $\lab_0$ is
$+$ and it is impossible to convert to any sealed symbolic values because the
next program statement requires the actual value stored in the variable $\varx$
for the branch condition $\varx \geq 0$.  Thus, it performs view transition
$\viewtrans{\lab_0}{\lab_1}$ from the label $\lab_0$ to another one $\lab_1$ for
the abstract value $+$ and the result is also $+$.  Now, the analysis element
$(\lab_1, +)$ could be converted to $\langle \symb \mapsto +, \symb \rangle$
with the label $\lab_1$.  This sealed symbolic execution step terminates in the
label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
operator requires the actual value of $\varx$.  Finally, it performs the view
transition and the result is $(\lab_4, -)$.

For the last case, we assume that all integers are possible for the initial
value of the variable $\varx$ as described in Figure~\ref{fig:ds-examples}(d).
While it reaches the false branch in the label $\lab_2$ unlike previous cases,
it also cannot perform dynamic shortcuts because the statement in the false
branch is $\varx = -\varx$.  At the label $\lab_3$, there is two analysis
elements: 1) $(\lab_3, +)$ introduced by view transition from the label $\lab_2$
with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_2$
introduced by sealed symbolic execution started at $\lab_1$.  However, since it
is not possible to perform sealed symbolic execution for both elements, the
second one is converted to $(\lab, 0+)$ and merged with $+$ at $\lab_3$ via the
join operator $\join$.  Finally, the view transition
$\viewtrans{\lab_3}{\lab_4}$ from $\lab_3$ to $\lab_4$ is performed to the
merged abstract state $0+$ and the result is $-0$.

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.15\textwidth}
    \includegraphics[height=3.2cm]{img/listing}
    \caption{Notations}
    \label{fig:ds-example1}
  \end{subfigure}
  \quad
  \begin{subfigure}[t]{0.23\textwidth}
    \includegraphics[height=3.2cm]{img/path-1}
    \caption{$\varx = 0$}
    \label{fig:ds-example2}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{img/path-2}
    \caption{$\varx > 0$}
    \label{fig:ds-example3}
  \end{subfigure}
  \begin{subfigure}[t]{0.28\textwidth}
    \includegraphics[height=3.2cm]{img/path-3}
    \caption{$\varx \in \mathbb{N}$}
    \label{fig:ds-example4}
  \end{subfigure}
  \caption{Abstract interpretation using a combined domain for the running
  example with different initial values for $\varx$.}
  \label{fig:ds-examples}
\end{figure*}

@@

\subsection{Examples}
Now, we show examples of abstract interpretation with a combined domain.
Figure~\ref{fig:ds-examples} depicts the flow of analysis for the running
example in Figure~\ref{fig:running-example} with three different initial sets of
values for the variable $\varx$.  In this example, we use the abstract domain
$\{ -, 0, + \}$ for integers stored in $\varx$ as introduced in
Section~\ref{sec:ai}, and the \textit{flow sensitivity} that utilizes the
labels of states as their views as introduced in Section~\ref{sec:sens}.
For brevity, we use concatenation of abstract values so that
$-0$ denotes the set $\{ -, 0 \}$.

Figure~\ref{fig:ds-examples}(a) presents notations used in each graph. A solid
box denotes an analysis element that is a pair of a label $\lab$ and an abstract
state $\abselem$.  A pair enclosed by angle brackets denotes an analysis
element that is a pair of an abstract instantiation map $\absimap$ and a sealed
symbolic state $\symbst$.  In fact, the sealed symbolic state part (right) of
each pair in graphs contains only the value of the variable of $\varx$ without
its label.  For brevity, we represent its label by locating it next to
a node with its label.  A solid line is a view transition
$\viewtrans{\lab}{\lab'}$ from a label $\lab$ to another one $\lab'$.  A dotted
line is a sealed symbolic transition $\symbtrans$.  Three solid lines with
circled labels denote two converters $\saconverter$, $\asconverter$ and the join
operator $\join$.

Figure~\ref{fig:ds-examples}(b) shows the analysis with the combined domain when
the initial value of $\varx$ is $0$.  First, in the \triagename step,
the converter $\asconverter$ converts the analysis element $(\lab_0, 0)$ to
another analysis element $\langle \varnothing, 0 \rangle$ with the label
$\lab_0$.  It does not introduce any sealed symbolic values because
the value represents only a single value.  Until the end of the program, the
sealed symbolic execution from $\langle \varnothing, 0 \rangle$ successfully
continues.  Because there is no more possible symbolic transition for the
symbolic state $\langle \varnothing, 0 \rangle$ with the label $\lab_4$,
it is converted to $(\lab_4, 0)$ via the converter $\saconverter$.

Instead of a single value, assume that the initial value of $\varx$ is one of
any positive integers.  Figure~\ref{fig:ds-examples}(c) describes the analysis
flow for the case.  The initial abstract value at the label $\lab_0$ is
$+$ and it is impossible to convert it to any sealed symbolic values because the
next program statement requires the actual value stored in the variable $\varx$
for the branch condition $\varx \geq 0$.  Thus, it performs view transition
$\viewtrans{\lab_0}{\lab_1}$ from the label $\lab_0$ to another one $\lab_1$ for
the abstract value $+$ and the result is also $+$.  Now, the analysis element
$(\lab_1, +)$ can be converted to $\langle \symb \mapsto +, \symb \rangle$
with the label $\lab_1$.  This sealed symbolic execution step terminates in the
label $\lab_3$ because the next statement is $\varx = -\varx$ and the negation
operator requires the actual value of $\varx$.  It is converted to $(\lab_3, +)$ via $\saconverter$,
performs the view transition, and results in $(\lab_4, -)$.

For the last case, we assume that all integers are possible for the initial
value of the variable $\varx$ as described in Figure~\ref{fig:ds-examples}(d).
While it reaches the false branch in the label $\lab_2$ unlike previous cases,
it cannot perform dynamic shortcuts because the statement in the false
branch is $\varx = -\varx$, which requires the actual value of $\varx$.
At the label $\lab_3$, there are two analysis
elements: 1) $(\lab_3, +)$ introduced by the view transition from the label $\lab_2$
with $-$, and 2) $\langle \symb \mapsto 0+, \symb \rangle$ with $\lab_3$
introduced by sealed symbolic execution started at $\lab_1$.  Since it
is not possible to perform sealed symbolic execution for both elements, the
second one is converted to $(\lab_3, 0+)$ and merged with $+$ at $\lab_3$ via the
join operator $\join$.  Finally, the view transition
$\viewtrans{\lab_3}{\lab_4}$ from $\lab_3$ to $\lab_4$ is performed to the
merged abstract state $0+$ and the result is $-0$.
